draft_group-6

### 2025-12-10 Paper.Rmd
Paper.Rmd

---
title: "draft_group-6"
author: "Sandra, Tigist, Mussa, Waddah"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

*Paper (40%)* A paper detailing the motivation, methodology, and results of your project, complete with references. (https://dsci445-csu.github.io/project/)

# Outline

>>>>

---
title: "draft_group-6"
author: "Sandra, Tigist, Mussa, Waddah"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
